A Convolutional Neural Network for Outsole Recognition\tnoteref{t1}

### 2019-06-24 paper/paper.Rnw
Finish draft of conclusion

\fix{DC moved to heatmap, green block text could still be removed}

@@

\section{Conclusions}
\svp{Rework this to address 3 main conclusions - 1: NNs work for automatic feature ID, 2: Different levels of feature variability within classes, and 3: correcting for contrast is important.}

@@

%\section{Future Work}
%\svp{Need to show image contrast stuff to use this paragraph.}
%Although CoNNOR performs well in its current state, there are still a number of ways to potentially improve prediction accuracy. For one, image contrast  plays a large role in how well the model classifies the geometric shapes present. Thus, exploring methods of color correction, such as histogram normalization, may prove useful for eliminating the effect of contrast on predictions. Geometric features are also relatively simple with respect to the features that are being detected by the final convolutional block of VGG16, as in \autoref{fig:vgg16layers}; it is quite possible that prediction accuracy could improve by directly classifying the features that are output by the fourth block, rather than using the full convolutional base.

>>>>

\fix{DC moved to heatmap, green block text could still be removed}
\fix{Write/check figure captions}

@@

\section{Conclusions}
%\svp{Rework this to address 3 main conclusions - 1: NNs work for automatic feature ID, 2: Different levels of feature variability within classes, and 3: correcting for contrast is important.}

@@

\fix{Although the model is not perfect in its current form, as a first pass tool it is performing well and improvements seem promising. That most of the misclassifications are systematic shows that the model is able to learn features and apply rules consistently. There are possible modifications to the labeling scheme that may make model predictions align more closely to human-assigned labels, but model consistency is a much higher good than ``accuracy" (in the sense of agreeing with human-assigned labels). Examiners themselves may vary in how to label ambiguous features (e.g., the half-rounded quadrilaterals in \fix{the dc heatmap}), so a consistent classification method provides a more unified definition of certain geometric shapes and facilitates comparison of outsoles with similar geometric features. All in all, this model shows that CNNS are a useful tool for classifying a large number of outsoles within a common classification scheme and can ultimately help streamline the current process of sorting and comparing shoes by class characteristics.}

\mt{I think the conclusion currently says everything I want it to (cutting off a conv block doesn't seem to help make the point). Definitely can use some language edits.}
